Experiment 2

### 2018-03-16 experiment_2/experiment_2.tex
updated comments

Comments: The story I seem to get from this is (roughly) that the worse the algorithm that the incumbent plays is, the better the entrant will do. Thus, the incumbent should want to play a better algorithm. However, in order for the entrant to do as well as possible, the entrant should in fact play a worse algorithm! This is interesting but I'm not sure it is intuitive.

>>>>

Comments: The story I seem to get from this is (roughly) that the worse the algorithm that the incumbent plays is, the better the entrant will do. Thus, the incumbent should want to play a better algorithm. However, in order for the entrant to do as well as possible, the entrant should in fact play a worse algorithm! If you think of it from the incumbent point of view, the incumbent is in the market first and so wants to learn as much as possible before the entrant comes in (thus does better with a better algorithm since it should have learned more by the time the entrant enters).  From the entrant point of view, since the incumbent has already learned something in order to have any chance to compete you do better by purely exploiting than by engaging in potentially suboptimal exploration. Two follow-up questions: Will this result hold if we run the simulations for more periods? What will happen to this result if we increase memory size?
